---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Unpack and load data:

```{r, echo=TRUE}
unzip("activity.zip")
data <- read.csv("activity.csv")
```

Transform data:

```{r, echo=TRUE}
data$date <- as.character(data$date)
```

## What is mean total number of steps taken per day?

```{r, echo=TRUE}
steps_per_date <- tapply(data$steps, data$date, sum, na.rm = T)
smean <- mean(steps_per_date)
smed <- median(steps_per_date)
```

Mean values is `r smean` and median values is `r smed`.

```{r, echo=TRUE}
hist(steps_per_date, xlab = "Steps taken per day")
abline(v = smean, lwd = 2, col = "green")
abline(v = smed, lwd = 2, col = "blue")
```

## What is the average daily activity pattern?

```{r, echo=TRUE}
avg_steps_per_date <- tapply(data$steps, data$interval, mean, na.rm = T)
max_avg_steps <- avg_steps_per_date[avg_steps_per_date == max(avg_steps_per_date)]
max_int <- as.numeric(names(max_avg_steps))
plot(x = row.names(avg_steps_per_date), y = avg_steps_per_date, type = "l", ylab = "Steps per interval", xlab = "Interval")
abline(v = max_int, lwd = 2, col = "green")
```

Maximum average number of steps is at interval `r max_int` with the number of steps is `r max_avg_steps`.

## Imputing missing values

```{r, echo=TRUE}
num_of_na <- sum(is.na(data$steps))
```

Number of missing data is a `r num_of_na`.

Use mean for current interval to fill data.

## Are there differences in activity patterns between weekdays and weekends?
